---
title: "Assignment I"
author: "Student Name"
date: "14/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1

```{r}
x = c(0, 2, 5, 3, 4, 5, 2, 4, 2, 2)
y = c(1, −1)
```

### (a)

x*y/sum(x)
R performs element wise operations:

each element of x will be multiplied with each element of y in a repeating fashing, with each result being divided by the sum of the x vector elements

```{r}
x1 = x*y/sum(x)
x1
```


### (b)

x^(1:length(y))

Length(y): returns the number of elements in vecto y
(1:length(y)):  generates a vector of elements 1 to Length(y)

x^(1:length(y)): powers each element of x with the corrending element in (1:length(y)) vector

```{r}
x2 = x^(1:length(y))
x2
```

## 2
### (a)

```{r}
x = pi
y = exp(1)
b = 2/3

ans = log(((x^2)*(y^4)/(x^2-y)^2), base=b)
ans
```

### (b)

```{r}
x = ( abs(1 - sqrt(pi))/(1 + tan(1.03)) )

ans = x^(1/4)
ans
```

## 3

```{r}
height = c(180, 165, 171, 160, 193, 175)
weight = c(87, 58, 65, NA, 100, 75)

bmi =  (weight/ (height/100)^2)
bmi
```

## 4

Draws a curve corresponding to a function over the interval [from, to]. curve can plot also an expression in the variable xname, default x.

```{r}
x = c(-1:1)
y = c(-0.8, 1.2)

fxp = (4/5)*(sqrt(abs(x)) + sqrt(1-x^2))
fxm = (4/5)*(sqrt(abs(x)) - sqrt(1-x^2))

curve( (4/5)*(sqrt(abs(x)) + sqrt(1-x^2)) )
curve( (4/5)*(sqrt(abs(x)) - sqrt(1-x^2)) )
```



## 5
```{r}
n = round(rnorm (1000, 500, 100), 2)
m = table( cut(n, seq( 0 , 1000, 200)) )
n
m

```

rnorm (1000, 500, 100):
random generation for the normal distribution with 1000 number of observations, mean of 500 and  standard deviations of 100.

round(rnorm (1000, 500, 100), 2):
rounds the values in its first argument to the specified number of decimal places, in this case 2 decimal points

seq( 0 , 1000, 200):
Generate regular sequences, from 0 to 1000 incremented by 200

cut(n, seq( 0 , 1000, 200)):
divides the range of n into  intervals and codes the values in n according to which interval they fall.

table( cut(n, seq( 0 , 1000, 200)) ):
uses the cross-classifying factors to build a contingency table of the counts at each combination of factor levels.

Code Variation:

```{r}
n = round(rnorm (100, 20, 100), 2)
m = table( cut(n, seq( 0 , 500, 50)) )
n
m
```





